\section{Experience}

\begin{enumerate}[leftmargin = 0pt, noitemsep]

\item[]{\cventry{July 2021--Present}{Tech Liaison, Harvest Intern, Reception and Guest Services}{Flowers Vineyard and Winery}{Healdsburg, CA}{}{
		\cvlistitem{Serve as on-site IT assistance, troubleshooting issues related to networks, hardware systems, and software.}
		\cvlistitem{Operate and setup machinery, sanitize equipment, and work independently to fulfill work orders.}
		\cvlistitem{Provide customer service and use professional software to organize seating, handle payments, and fill orders.}
}}

%\item[]{\cventry{February 2021--Present}{Lifeguard}{City of Rohnert Park}{Rohnert Park, CA}{}{
%		\cvlistitem{Customer service, payment handling, chemical and facility checks, assist customers and patrons. }
		%\cvlistitem{Maximized customer satisfaction by maintaining a positive attitude and resolving any issues promptly.}
%		\cvlistitem{Communicate pool and city policies to guests and resolve any customer or safety issues. }
%}}

\item[]{\cventry{November 2020--February 2021}{Temporary Laboratory Technician}{Clover Sonoma Farms}{Petaluma, CA}{}{
		\cvlistitem{Prepared and analyzed laboratory samples, testing for a microbial presence, and reported the data.}
			%Used and updated laboaratory database and performed calculations on vitamin content.}
	\cvlistitem{Checked equipment, calculated vitamin content, sanitized, restocked, and swabbed equipment for microbes.}
}}

\item[]{\cventry{October 2019--June 2020}{Engineering Tutor}{Academic Assistance and Tutoring Centers, UC Davis}{Davis, CA}{}{
		\cvlistitem{Recruited by the AATC to tutor classical and modern physics, electrical engineering, and computer science.}
		\cvlistitem{Tutored individuals and groups, in person and remotely. Prepared practice problems and learning software.}
		%\cvlistitem{Prepared learning materials, such as practice problems and example software to assist student’s learning.}
		%\cvlistitem{Tutored individuals and groups in classical physics, modern physics, computer science, and engineering.}
		%\cvlistitem{Practiced mixed-media educational tactics to accommodate students with a diverse set of learning habits.}
}}

%\item[]{\cventry{January 2020--March 2020}{Selected Undergraduate}{Special Study for Advanced Undergraduates, UC Davis}{Davis, CA}{}{
		%\cvlistitem{I researched credit card fraud  of a cyber security professor.}
%		\cvlistitem{Designed and implemented an algorithm that used a phone camera to recognize a name from a bank card.}
%		\cvlistitem{Presented and demonstrated my research and algorithm to faculty in cybersecurity as well as my colleagues.}
%}}

\item[]{\cventry{May 2019--November 2019}{Lead}{Moving With Grace}{Woodland, CA}{}{
	\cvlistitem{Lead moving crews, managed supplies and equipment, interacted directly clients, and handled payments.}
	\cvlistitem{Assembled and dissembled items, labeled and organized packaging for shipping and long term storage.}
}}

\item[]{\cventry{September 2018--June 2019}{Aggie Host Security}{UC Davis Police Department}{Davis, CA}{}{
		\cvlistitem{Public outreach and security at events, drove for the Safe Ride service, and patrolled university property.}
	\cvlistitem{Greeted and provided services to visitors of the university at sporting events, commencements, and concerts.} 
	%\cvlistitem{Drove for the Safe Ride service, conducted security patrols of university buildings and campus apartments.}
}}


\item[]{\cventry{June 2018--April 2019}{Research Intern}{UC Davis Computer Science Department}{Davis, CA}{}{
		\cvlistitem{Worked on an academic research project. Read research papers and presented findings, progress, and ideas.}
		%\cvlistitem{Worked alongside faculty and grad students studying the security of a Science DMZ network.}
		\cvlistitem{Setup a computer and used Bro/Zeek and Snort to collect and analyze network data for experiments.}
		%\cvlistitem{Set up a computer and used Bro/Zeek and Snort to collect data on network traffic for experiments.}
		%\cvlistitem{I gained experience using and understanding professional security software such as Bro/Zeek and Snort.}
}}

\item[]{\cventry{April 2016--June 2018}{Resident Advisor}{UC Davis Student Housing}{Davis, CA}{}{
 	\cvlistitem{Assisted, advised, and counseled students, mediated conflict, responded to crisis, and enforced policies.}
	\cvlistitem{Managed up to 110 residents, planned events, and communicated with students from various backgrounds.}
}}

%\item[]{\cventry{Summer 2016}{Cadet}{UC Davis Student Fire Fighter Academy}{Davis, CA}{}{
%	\cvlistitem{I learned a variety of skills such as teamwork, discipline, and properly handling and maintaining equipment}
%	\cvlistitem{Trained in fire fighting techniques, SCBA operation, physical fitness, emergency and crisis response}
%}}

%\item[]{\cventry{March 2012--September 2015}{Cadet, Petty Officer}{U.S. Naval Sea Cadet Corps}{Petaluma, CA}{}{
%	\cvlistitem{Represented the organization at events such as Fleet Week in San Francisco and the Santa Rosa Air Show}
%	\cvlistitem{Several hundred hours of community service while leading a team of up to 25 individuals, as a senior cadet}
%}}

\end{enumerate}